The Error Estimate of Force Calculation in the Inhomogeneous Molecular Systems

### 2011-11-16 shortRange.inhomo/writeDown/main.tex
small improvments

The widely accepted definition of the force error is the \emph{root
  mean square} (RMS) \emph{error}, which is the square root of the second
moment of the error force $\mathcal E(\v r) =
\sqrt{\langle\vert\Delta\v F(\v r)\vert^2\rangle}$. This is 
calculated as:
\begin{align} \nonumber
  \langle\vert\Delta\v F(\v r)\vert^2\rangle
  =\,&
  \big\langle\sum_{j,k}\v f^c(\v r - \v r_j)\cdot\v f^c(\v r - \v r_k)\big\rangle \\ \nonumber
  =\,&
  \big\langle\sum_j\vert\v f^c(\v r - \v r_j)\vert^2\big\rangle +
  \big\langle\sum_{j\neq k}\v f^c(\v r - \v r_j)\cdot\v f^c(\v r - \v r_k)\big\rangle \\ \nonumber
  =\,&
  \int_{\mathbb R^3}\vert\v f^c(\v r - \v r')\vert^2\rho(\v r')\,\d d\v r'
  + \\\label{eqn:tmp4}
  \,&
  \int_{\mathbb R^3\times\mathbb R^3}\v f^c(\v r - \v r')\cdot\v f^c(\v r - \v r'')\rho(\v r', \v r'')\,\d d\v r'\d d\v r''.
\end{align}
Where  $\rho(\v r', \v r'')$ is the pair density. By using the identity
\begin{align}  \label{eqn:tmp7}
  \rho(\v r', \v r'')
  = \rho(\v r')\rho(\v r'') + C (\v r', \v r''),
\end{align}
where 
\begin{align}
C (\v r', \v r'') = [\,\rho(\v r', \v r'') -  \rho(\v r')\rho(\v r'')\,]
\end{align}
denotes the density correlation between position $\v r'$ and $\v
r''$. Eqn. \eqref{eqn:tmp4} becomes
\begin{align} \nonumber
  \langle\vert\Delta\v F(\v r)\vert^2\rangle
  = &\,
  \int_{\mathbb R^3}\vert\v f^c(\v r - \v r')\vert^2\rho(\v r')\,\d d\v r' \,+ \\\nonumber
  &\,
  \bigg[\int_{\mathbb R^3}\v f^c(\v r - \v r')\rho(\v r')\,\d d\v r'\,\bigg]^2 + \\\nonumber
  &\,
  \int_{\mathbb R^3\times\mathbb R^3}\v f^c(\v r - \v r')\cdot\v f^c(\v r - \v r'')\,C(\v r', \v r'')\,\d d\v r'\d d\v r'' \\\label{eqn:tmp5}
  = &\,
  \mathcal E^2_{\textrm{homo}}(\v r) +
%  \langle\Delta\v F(\v r)\,\rangle^2 +
  \mathcal E^2_{\textrm{inhomo}}(\v r) +
  \mathcal E^2_{\textrm{correlation}}(\v r).
\end{align}
If the system is homogeneous and the particle-particle correlation is
neglected, then only the first term is left on the right hand side of \eqref{eqn:tmp5}, so it
is called the homogeneity error.  This term originates from the
fluctuation of the error force $\Delta\v F(\v r)$.  The second term is
called the inhomogeneity error, because it stems from the density
inhomogeneity of the system. It is worth pointing out that the
inhomogeneity error is nothing but the magnitude of the mean error force,
namely $\mathcal E_{\textrm{inhomo}}(\v r) = \vert\langle\Delta\v F(\v
r)\,\rangle\vert$.  The last term on right hand side of \eqref{eqn:tmp5} originates from the
correlation between the particles, so it is called the correlation
error.
The correlation error involves a double integral, which
implies that the calculation  requires more compuational resources
than the homogeneity and inhomogeneity errors.
The rest of this paper
assumes the 
correlation error does not dominate in the system, and can be safely
neglected.
It is worth pointing out that this is not always true, for example, in
critical region where the corrlation plays an important role in the system,
the corrlation error should be taken into account.

@@

The naive calculation of the convolutions in the error estimate \eqref{eqn:tmp5} requires
a computational cost of $\mathcal O(N^2)$. To estimate the force error
on the fly, the computational cost of the estimate should be reduced to
at least $\mathcal O(N\log N)$.  This is achieved by  using the fast Fourier transform. We
assume the simulation box is uniformly divided in to small bins.  The
positions of these bins are
\begin{align}
  \v r_{i_1, i_2, i_3} & =
  \frac{i_1}{K_1}\v a_1 + 
  \frac{i_2}{K_2}\v a_2 + 
  \frac{i_3}{K_3}\v a_3,\qquad 0\leq i_\alpha< K_\alpha
\end{align}
where $\v a_\alpha$ are box vectors, and $K_\alpha$ is the number of
division on each direction. In the reciprocal space, a corresponding
lattice is set up:
\begin{align}
  \v k_{k_1, k_2, k_3} & =
  k_1\v a_1^\ast +
  k_2\v a_2^\ast +
  k_3\v a_3^\ast, \qquad 0\leq k_\alpha<K_\alpha
\end{align}
where $\v a_\alpha^\ast$ are reciprocal box vectors defined by $\v
a_\alpha\cdot\v a_\beta^\ast = \delta_{\alpha\beta}$.  In each bin the
error and the particles number density are assumed to be constant,
then, a Fourier expansion can be obtained:
\begin{align}\nonumber
  \mathcal E^2_{\textrm{homo}}(\v r_{i_1,i_2,i_3})
  & =
  \frac1V\sum_{k_1=-\infty}^\infty\sum_{k_2=-\infty}^\infty\sum_{k_3=-\infty}^\infty
  [{\mathcal E}^2_{\textrm{homo}}]^{\wedge}(\v k_{k_1,k_2,k_3})
  % e^{2\pi i\v k_{k_1,k_2,k_3}\cdot\v r_{i_1,i_2,i_3}}
  \exp\bigg[
  2\pi i\bigg(
  \frac{k_1i_1}{K_1} + \frac{k_2i_2}{K_2} + \frac{k_3i_3}{K_3}
  \bigg)
  \bigg] \\\label{eqn:tmp13}
  & =
  \frac1V\sum_{k_1=0}^{K_1}\sum_{k_2=0}^{K_2}\sum_{k_3=0}^{K_3}
  \hat{K}_{\textrm{homo}}(\v k'_{k_1,k_2,k_3})\:
  \hat{\rho}(\v k_{k_1,k_2,k_3})
  % e^{2\pi i\v k_{k_1,k_2,k_3}\cdot\v r_{i_1,i_2,i_3}}
  \exp\bigg[
  2\pi i\bigg(
  \frac{k_1i_1}{K_1} + \frac{k_2i_2}{K_2} + \frac{k_3i_3}{K_3}
  \bigg)
  \bigg].
\end{align}
Here $\vert\v f^c(\v r)\vert^2$ is denoted by
$K_{\textrm{homo}}(\v r)$.
The wedge notation $\wedge$ means Fourier transform. The prime on $\v k_{k_1,k_2,k_3}$ means
that the periodic image $k_\alpha - K_\alpha$ should use instead of
$k_\alpha$ when $k_\alpha \geq K_\alpha/2$.
The second equation in \eqref{eqn:tmp13}
holds due to the fact:
$[\mathcal E^2]^\wedge = [K_{\textrm{homo}}\ast\rho]^\wedge = \hat{K}_{\textrm{homo}} \times \hat\rho$. The Fourier transform of $\rho$ and $K_{\textrm{homo}}$  are
\begin{align}
  \hat\rho(\v k_{k_1,k_2,k_3})
  & =
  \frac{V}{K_1K_2K_3}
  \sum_{i_1=0}^{K_1}\sum_{i_2=0}^{K_2}\sum_{i_2=0}^{K_2}
  \rho(\v r_{i_1,i_2,i_3})
  \exp\bigg[
  -2\pi i\bigg(
  \frac{k_1i_1}{K_1} + \frac{k_2i_2}{K_2} + \frac{k_3i_3}{K_3}
  \bigg)
  \bigg],
\end{align}
and
\begin{align}\label{eqn:f-kernel-homo}
  \hat K_{\textrm{homo}}(\v k)
  &=
  \int_{\mathbb R^3}K_{\textrm{homo}}(\v s)e^{-2\pi i\v k\cdot\v s}\,\d d\v s.
\end{align}
Most of the short-range
interactions are isotropic, so  $K_{\textrm{homo}}(\v r) =
K_{\textrm{homo}}(r)$, then the three-dimensional integral in
Eqn. \eqref{eqn:f-kernel-homo} can be simplified to a one-dimensional
integral:
\begin{align}\label{eqn:kernel-inte}
  \hat{K}_{\textrm{homo}}(\v k)
  =
  % \int_{\mathbb R^3}K_{\textrm{homo}}(r)e^{-2\pi i\v k\cdot\v r}\d d\v r
  % =
  \int_{r_c}^\infty \frac{2 s}k\, K_{\textrm{homo}}(s) \sin(2\pi ks)\,\d ds,
\end{align}
which can be calculated by numerical
integration from $r_c$ to a large upper bound, saying $R_c$. Perfect
convergence can be achieved by using $R_c = 30\sigma$ throughout the
paper. Since integral \eqref{eqn:kernel-inte} is independent of the
density of the system, it is calculated only once and stored.

@@

To make the adaptive cut-off method feasible, we assume:
\begin{enumerate}
\item The space is uniformly divided in to small bins, the size of which is the
  same as those mentioned in the section \ref{sec:tmp1.3}.  The
  particles falling in the same bin are assigned the same cut-off
  radius. In other words, the cut-off radius is chosen for each bin
  rather than for each particles.
  % The cut-off
  % radius is assumed to be constant within a bin, no matter the
  % position of the partile.
\item The cut-off radius can only be chosen from a discrete series of
  monotonically increasing values between a maximum 
  $r_c^{\textrm{max}}$ and a minimum 
  $r_c^{\textrm{min}}$: $\{\,r_c^{\textrm{min}} = r_c^0 < r_c^1 <
  \cdots < r_c^{M-1} <r_c^M = r_c^{\textrm{max}}\}$.  We call it the
  \emph{candidate set} of the cut-off radius.  For convenience but not
  necessarily, the cut-off radii in the candidate set is uniformly increasing, i.e.
  \begin{align}
    r_c^m = r_c^0 + r_c^{\textrm{step}} m, \quad 0 \leq m \leq M.
  \end{align}
  For example, a possible candidate set is $\{2.5\,\sigma,\
  3.0\,\sigma,\ 3.5\,\sigma,\ 4.0\,\sigma,\ \cdots,\ 10.0\,\sigma\}$,
  with $r_c^{\textrm{max}} = 10.0\sigma$, $r_c^{\textrm{min}} =
  2.5\sigma$ and $r_c^{\textrm{step}} = 0.5 \sigma$.
\end{enumerate}
For each cut-off radius in the candidate set, the force error
$\mathcal E(\v r)$ is calculated by the estimate Eqn.~\eqref{eqn:tmp5}.
Notice the error is calculated by the
fast algorithm described in section~\ref{sec:tmp1.3}, so it is
defined on the bins.  For a predetermined error control level
$\mathcal E_{\textrm{C}}$, a satisfactory cut-off radius for a bin is
chosen such that it is the smallest one satisfying the precision
constrain $\mathcal E(\v r_{i_1,i_2,i_3}) \leq \mathcal
E_{\textrm{C}}$. The computational cost of this algorithm is $\mathcal
O(MN\log N)$.  The idea of this algorithm is based on the observation
that the cut-off radius may not be calculated at a very high
precision, a slightly (at most $r_c^{\textrm{step}}$) larger
cut-off radius will not waste too much computational cost.  Due to the
thermodynamic fluctuation of the particle density, the resulting cut-off
distribution $r_c(\v r_{i_1,i_2,i_3})$ (as a function of bin
position) needs to be refined by the following scheme:
\begin{align}\label{eqn:rc-refine}
  r^{(1)}_c(\v r_{i_1,i_2,i_3}) = \max_{j_\alpha\in I}\,r_c(\v r_{i_1+j_1,i_2+j_2,i_3+j_3}),
  \quad I = \{-1, 0, 1\},
\end{align}
so that the fluctuating large-error regions are safely covered by bins
with large cut-off radius.

@@

In an inhomogeneous system, the inhomogeneity error may play a
dominate role in the simulation, (see examples in section~\ref{sec:tmp2}).
Since the mean error force can be calculated
by Eqn.~\eqref{eqn:tmp17} on the fly, a simple way to screen out the
inhomogeneity error is to correct the computed force by the mean error
force, namely
\begin{align}\label{eqn:define-fcorr}
  \v F_{\textrm{corr}}(\v r) = \tilde{\v F}(\v r) + \langle\Delta\v F(\v r)\rangle.
\end{align}
In this paper, the mean error force $\langle\Delta\v F(\v r)\rangle$
is also refered as \emph{correction force} in the context of
long-range force correction. This correction works because it takes
into account the force contribution outside the cut-off radius. The mean of
the corrected error force vanishes:
\begin{align}\label{eqn:mean-fcorr}
  \langle\Delta\v F_{\textrm{corr}}(\v r)\rangle
   =
  \big\langle\,
  \v F(\v r) - \tilde{\v F}(\v r) - \langle\Delta\v F(\v r)\rangle\,
  \big\rangle = 0.
\end{align}
The mean square error is given by
\begin{align} \nonumber
  \langle\vert\Delta\v F_{\textrm{corr}}(\v r)\vert^2\rangle
  & =
  \big\langle\,
  [\,\v F(\v r) - \tilde{\v F}(\v r) - \langle\Delta\v F(\v r)\rangle\,]^2
  \big\rangle \\\nonumber
  & =
  \big\langle\,
  [\,\Delta\v F(\v r) - \langle\Delta\v F(\v r)\rangle\,]^2
  \big\rangle \\\nonumber
  & =
  \langle\vert\Delta\v F(\v r)\vert^2\rangle -
  \langle\Delta\v F(\v r)\,\rangle^2 \\
  & =
  \mathcal E^2_{\textrm{homo}}(\v r) +
  \mathcal E^2_{\textrm{correlation}}(\v r),
\end{align}
containing no inhomogeneity contribution.  It is worth noticing that the mean
square error of the corrected force is nothing but the variance of the
error force: $\langle\vert\Delta\v
F_{\textrm{corr}}(\v r)\vert^2\rangle = \textrm{Var}[\Delta\v
F_{\textrm{corr}}(\v r)] = \textrm{Var}[\Delta\v F(\v r)]$.

>>>>

The widely accepted definition of the force error is the \emph{root
  mean square} (RMS) \emph{error}, which is the square root of the second
moment of the error force $\mathcal E(\v r) =
\sqrt{\langle\vert\Delta\v F(\v r)\vert^2\rangle}$. This is 
calculated as:
\begin{align} \nonumber
  \langle\vert\Delta\v F(\v r)\vert^2\rangle
  =\,&
  \big\langle\sum_{j,k}\v f^c(\v r - \v r_j)\cdot\v f^c(\v r - \v r_k)\big\rangle \\ \nonumber
  =\,&
  \big\langle\sum_j\vert\v f^c(\v r - \v r_j)\vert^2\big\rangle +
  \big\langle\sum_{j\neq k}\v f^c(\v r - \v r_j)\cdot\v f^c(\v r - \v r_k)\big\rangle \\ \nonumber
  =\,&
  \int_{\mathbb R^3}\vert\v f^c(\v r - \v r')\vert^2\rho(\v r')\,\d d\v r'
  + \\\label{eqn:tmp4}
  \,&
  \int_{\mathbb R^3\times\mathbb R^3}\v f^c(\v r - \v r')\cdot\v f^c(\v r - \v r'')\rho(\v r', \v r'')\,\d d\v r'\d d\v r''.
\end{align}
Where  $\rho(\v r', \v r'')$ is the pair density. By using the identity
\begin{align}  \label{eqn:tmp7}
  \rho(\v r', \v r'')
  = \rho(\v r')\rho(\v r'') + C (\v r', \v r''),
\end{align}
where 
\begin{align}
C (\v r', \v r'') = [\,\rho(\v r', \v r'') -  \rho(\v r')\rho(\v r'')\,]
\end{align}
denotes the density correlation between position $\v r'$ and $\v
r''$. Eqn. \eqref{eqn:tmp4} becomes
\begin{align} \nonumber
  \langle\vert\Delta\v F(\v r)\vert^2\rangle
  = &\,
  \int_{\mathbb R^3}\vert\v f^c(\v r - \v r')\vert^2\rho(\v r')\,\d d\v r' \,+ \\\nonumber
  &\,
  \bigg[\int_{\mathbb R^3}\v f^c(\v r - \v r')\rho(\v r')\,\d d\v r'\,\bigg]^2 + \\\nonumber
  &\,
  \int_{\mathbb R^3\times\mathbb R^3}\v f^c(\v r - \v r')\cdot\v f^c(\v r - \v r'')\,C(\v r', \v r'')\,\d d\v r'\d d\v r'' \\\label{eqn:tmp5}
  = &\,
  \mathcal E^2_{\textrm{homo}}(\v r) +
%  \langle\Delta\v F(\v r)\,\rangle^2 +
  \mathcal E^2_{\textrm{inhomo}}(\v r) +
  \mathcal E_{\textrm{correlation}}(\v r).
\end{align}
If the system is homogeneous and the particle-particle correlation is
neglected, then only the first term is left on the right hand side of \eqref{eqn:tmp5}, so it
is called the homogeneity error.  This term originates from the
fluctuation of the error force $\Delta\v F(\v r)$.  The second term is
called the inhomogeneity error, because it stems from the density
inhomogeneity of the system. It is worth pointing out that the
inhomogeneity error is nothing but the magnitude of the mean error force,
namely $\mathcal E_{\textrm{inhomo}}(\v r) = \vert\langle\Delta\v F(\v
r)\,\rangle\vert$.  The last term on right hand side of \eqref{eqn:tmp5} originates from the
correlation between the particles, so it is called the correlation
error.
The correlation error involves a double integral, which
implies that the calculation  requires more compuational resources
than the homogeneity and inhomogeneity errors.
The rest of this paper
assumes the 
correlation error does not dominate in the system, and can be safely
neglected.
It is worth pointing out that this is not always true, for example, in
critical region where the corrlation plays an important role in the system,
the corrlation error should be taken into account.

@@

The naive calculation of the convolutions in the error estimate \eqref{eqn:tmp5} requires
a computational cost of $\mathcal O(N^2)$. To estimate the force error
on the fly, the computational cost of the estimate should be reduced to
at least $\mathcal O(N\log N)$.  This is achieved by  using the fast Fourier transform. We
assume the simulation box is uniformly divided in to small bins.  The
positions of these bins are
\begin{align}
  \v r_{i_1, i_2, i_3} & =
  \frac{i_1}{K_1}\v a_1 + 
  \frac{i_2}{K_2}\v a_2 + 
  \frac{i_3}{K_3}\v a_3,\qquad 0\leq i_\alpha< K_\alpha
\end{align}
where $\v a_\alpha$ are box vectors, and $K_\alpha$ is the number of
division on each direction. In the reciprocal space, a corresponding
lattice is set up:
\begin{align}
  \v k_{k_1, k_2, k_3} & =
  k_1\v a_1^\ast +
  k_2\v a_2^\ast +
  k_3\v a_3^\ast, \qquad 0\leq k_\alpha<K_\alpha
\end{align}
where $\v a_\alpha^\ast$ are reciprocal box vectors defined by $\v
a_\alpha\cdot\v a_\beta^\ast = \delta_{\alpha\beta}$.  In each bin the
error and the particles number density are assumed to be constant,
then, a Fourier expansion can be obtained:
\begin{align}\nonumber
  \mathcal E^2_{\textrm{homo}}(\v r_{i_1,i_2,i_3})
  & =
  \frac1V\sum_{k_1=-\infty}^\infty\sum_{k_2=-\infty}^\infty\sum_{k_3=-\infty}^\infty
  [{\mathcal E}^2_{\textrm{homo}}]^{\wedge}(\v k_{k_1,k_2,k_3})
  % e^{2\pi i\v k_{k_1,k_2,k_3}\cdot\v r_{i_1,i_2,i_3}}
  \exp\bigg[
  2\pi i\bigg(
  \frac{k_1i_1}{K_1} + \frac{k_2i_2}{K_2} + \frac{k_3i_3}{K_3}
  \bigg)
  \bigg] \\\label{eqn:tmp13}
  & =
  \frac1V\sum_{k_1=0}^{K_1}\sum_{k_2=0}^{K_2}\sum_{k_3=0}^{K_3}
  \hat{K}_{\textrm{homo}}(\v k'_{k_1,k_2,k_3})\:
  \hat{\rho}(\v k_{k_1,k_2,k_3})
  % e^{2\pi i\v k_{k_1,k_2,k_3}\cdot\v r_{i_1,i_2,i_3}}
  \exp\bigg[
  2\pi i\bigg(
  \frac{k_1i_1}{K_1} + \frac{k_2i_2}{K_2} + \frac{k_3i_3}{K_3}
  \bigg)
  \bigg].
\end{align}
Here $K_{\textrm{homo}}(\v r)$ denotes $\vert\v f^c(\v r)\vert^2$.
The wedge notation $\wedge$ means Fourier transform. The prime on $\v k_{k_1,k_2,k_3}$ means
that the periodic image $k_\alpha - K_\alpha$ should use instead of
$k_\alpha$ when $k_\alpha \geq K_\alpha/2$.
The second equation in \eqref{eqn:tmp13}
holds due to the fact:
$[\mathcal E^2]^\wedge = [K_{\textrm{homo}}\ast\rho]^\wedge = \hat{K}_{\textrm{homo}} \times \hat\rho$. The Fourier transform of $\rho$ and $K_{\textrm{homo}}$  are
\begin{align}
  \hat\rho(\v k_{k_1,k_2,k_3})
  & =
  \frac{V}{K_1K_2K_3}
  \sum_{i_1=0}^{K_1}\sum_{i_2=0}^{K_2}\sum_{i_2=0}^{K_2}
  \rho(\v r_{i_1,i_2,i_3})
  \exp\bigg[
  -2\pi i\bigg(
  \frac{k_1i_1}{K_1} + \frac{k_2i_2}{K_2} + \frac{k_3i_3}{K_3}
  \bigg)
  \bigg],
\end{align}
and
\begin{align}\label{eqn:f-kernel-homo}
  \hat K_{\textrm{homo}}(\v k)
  &=
  \int_{\mathbb R^3}K_{\textrm{homo}}(\v s)e^{-2\pi i\v k\cdot\v s}\,\d d\v s.
\end{align}
Most of the short-range
interactions are isotropic, i.e. $K_{\textrm{homo}}(\v r) =
K_{\textrm{homo}}(r)$, then the three-dimensional integral in
Eqn. \eqref{eqn:f-kernel-homo} can be simplified to a one-dimensional
integral:
\begin{align}\label{eqn:kernel-inte}
  \hat{K}_{\textrm{homo}}(\v k)
  =
  % \int_{\mathbb R^3}K_{\textrm{homo}}(r)e^{-2\pi i\v k\cdot\v r}\d d\v r
  % =
  \int_{r_c}^\infty \frac{2 s}k\, K_{\textrm{homo}}(s) \sin(2\pi ks)\,\d ds,
\end{align}
which can be calculated by numerical
integration from $r_c$ to a large upper bound, saying $R_c$. Perfect
convergence can be achieved by using $R_c = 30\sigma$ throughout the
paper. Since integral \eqref{eqn:kernel-inte} is independent of the
density of the system, it is calculated only once and stored.

@@

To make the adaptive cut-off method feasible, we assume:
\begin{enumerate}
\item The space is uniformly divided in to small bins, the size of which is the
  same as those mentioned in the section \ref{sec:tmp1.3}.  The
  particles falling in the same bin are assigned the same cut-off
  radius. In other words, the cut-off radius is chosen for each bin
  rather than for each particles.
  % The cut-off
  % radius is assumed to be constant within a bin, no matter the
  % position of the partile.
\item The cut-off radius can only be chosen from a discrete series of
  monotonically increasing values between a maximum 
  $r_c^{\textrm{max}}$ and a minimum 
  $r_c^{\textrm{min}}$: $\{\,r_c^{\textrm{min}} = r_c^0 < r_c^1 <
  \cdots < r_c^{M-1} <r_c^M = r_c^{\textrm{max}}\}$.  We call it the
  \emph{candidate set} of the cut-off radius.  For convenience but not
  necessarily, the cut-off radii in the candidate set is uniformly increasing, i.e.
  \begin{align}
    r_c^m = r_c^0 + r_c^{\textrm{step}} m, \quad 0 \leq m \leq M.
  \end{align}
  For example, a possible candidate set is $\{2.5\,\sigma,\
  3.0\,\sigma,\ 3.5\,\sigma,\ 4.0\,\sigma,\ \cdots,\ 10.0\,\sigma\}$,
  with $r_c^{\textrm{max}} = 10.0\sigma$, $r_c^{\textrm{min}} =
  2.5\sigma$ and $r_c^{\textrm{step}} = 0.5 \sigma$.
\end{enumerate}
For each cut-off radius in the candidate set, the force error
$\mathcal E(\v r)$ is calculated by the estimate Eqn.~\eqref{eqn:tmp5}.
Notice the error is calculated by the
fast algorithm described in section~\ref{sec:tmp1.3}, so it is
defined on the bins.  For a predetermined error control level
$\mathcal E_{\textrm{C}}$, a satisfactory cut-off radius for a bin is
chosen such that it is the smallest one satisfying the precision
constraint $\mathcal E(\v r_{i_1,i_2,i_3}) \leq \mathcal
E_{\textrm{C}}$. The computational cost of this algorithm is $\mathcal
O(MN\log N)$.  The idea of this algorithm is based on the observation
that the cut-off radius may not be calculated at a very high
precision, a slightly (at most $r_c^{\textrm{step}}$) larger
cut-off radius will not waste too much computational cost.  Due to the
thermodynamic fluctuation of the particle density, the resulting cut-off
distribution $r_c(\v r_{i_1,i_2,i_3})$ (as a function of bin
position) needs to be refined by the following scheme:
\begin{align}\label{eqn:rc-refine}
  r^{(1)}_c(\v r_{i_1,i_2,i_3}) = \max_{j_\alpha\in I}\,r_c(\v r_{i_1+j_1,i_2+j_2,i_3+j_3}),
  \quad I = \{-1, 0, 1\},
\end{align}
so that the fluctuating large-error regions are safely covered by bins
with large cut-off radius.

@@

In an inhomogeneous system, the inhomogeneity error may play a
dominate role in the simulation, (see examples in section~\ref{sec:tmp2}).
Since the mean error force can be calculated
by Eqn.~\eqref{eqn:tmp17} on the fly, a simple way to screen out the
inhomogeneity error is to correct the computed force by the mean error
force, namely
\begin{align}\label{eqn:define-fcorr}
  \v F_{\textrm{corr}}(\v r) = \tilde{\v F}(\v r) + \langle\Delta\v F(\v r)\rangle.
\end{align}
In this paper, the mean error force $\langle\Delta\v F(\v r)\rangle$
is also refered as \emph{correction force} in the context of
long-range force correction. This correction works because it takes
into account the force contribution outside the cut-off radius. The mean of
the corrected error force vanishes:
\begin{align}\label{eqn:mean-fcorr}
  \langle\Delta\v F_{\textrm{corr}}(\v r)\rangle
   =
  \big\langle\,
  \v F(\v r) - \tilde{\v F}(\v r) - \langle\Delta\v F(\v r)\rangle\,
  \big\rangle = 0.
\end{align}
The mean square error is given by
\begin{align} \nonumber
  \langle\vert\Delta\v F_{\textrm{corr}}(\v r)\vert^2\rangle
  & =
  \big\langle\,
  [\,\v F(\v r) - \tilde{\v F}(\v r) - \langle\Delta\v F(\v r)\rangle\,]^2
  \big\rangle \\\nonumber
  & =
  \big\langle\,
  [\,\Delta\v F(\v r) - \langle\Delta\v F(\v r)\rangle\,]^2
  \big\rangle \\\nonumber
  & =
  \langle\vert\Delta\v F(\v r)\vert^2\rangle -
  \langle\Delta\v F(\v r)\,\rangle^2 \\
  & =
  \mathcal E^2_{\textrm{homo}}(\v r) +
  \mathcal E_{\textrm{correlation}}(\v r),
\end{align}
containing no inhomogeneity contribution.  It is worth noticing that the mean
square error of the corrected force is nothing but the variance of the
error force: $\langle\vert\Delta\v
F_{\textrm{corr}}(\v r)\vert^2\rangle = \textrm{Var}[\Delta\v
F_{\textrm{corr}}(\v r)] = \textrm{Var}[\Delta\v F(\v r)]$.
